---
title: "About (Draft)"
author: "Elizabeth Guo"
date: "10/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readxl)
library(janitor)
library(tidyverse)
```

```{r data downloading and processing}

justicesdata <- read_xlsx("raw-data/justicesdata.xlsx")

justice_Docket <- read_xlsx("raw-data/SCDB_2019_01_justiceCentered_Docket.xlsx") %>% 
  clean_names()

```

## The Project

Currently, sitting on the bench of the U.S. Supreme Court are 5 Catholic justices, 3 Jewish justices, and 1 Episcopalian justice. But this religious makeup would have been unthinkable just 100 years ago in a nation with deeply entrenched roots in Protestant Christianity. What changed, and when? This project examines the changing demographic makeup - including age, educational background, birth city and more - of the nine Supreme Court justices from 1789 to the present. Furthermore, this project seeks to draw connections bewteen shifts in Court demographics over time with shifting political tides and events in U.S. history. 

## The Data

Data used in this project comes from Washington University of St. Louis' Professor Lee Epstein's U.S. Supreme Court Database. This public database was last updated on July 30, 2019 and includes data on all U.S. Supreme Court nominees (including those unconfirmed). I will focus on the justices who were confirmed and served on the Court.

Citation: Epstein, Lee, Thomas G. Walker, Nancy Staudt, Scott Hendrickson, and Jason Roberts. (2019). "The U.S. Supreme Court Justices Database." February 11. At: http://epstein.wustl.edu/research/justicesdata.html.

Data also comes from Washington University Law's Supreme Court Database. Information on justices and legal provisions was found from this database.

Citation: Harold J. Spaeth, Lee Epstein, Andrew D. Martin, Jeffrey A. Segal, Theodore J. Ruger, and Sara C. Benesh. 2019 Supreme Court Database, Version 2019 Release 01. URL: http://Supremecourtdatabase.org. 

## About Elizabeth Guo

I am a sophomore at Harvard concentrating in Physics & Mathematics with a secondary in Government. I am very interested in the intersection of law and the quantitative. Contact me at elizabethguo@college.harvard.edu. 


